\newpage\phantomsection
\begin{thebibliography}{99}
\bibitem{SA_SA} Sahai, H., Ageel, M.I. [2000], The Analysis of Variance: Fixed, Random and Mixed Models, Birkh\"auser.
\bibitem{SA_KNNL} Kutner, M.H., Nachtsheim, C.J., Neter, J, Li. W. Ageel, M.I. [2004], Applied Linear Statistical Models, 5th ed., McGraw-Hill-Irwin. 
\bibitem{SA_HW} Hollander, M., Wolfe, D.A. [1999], Nonparametric Statistical Methods, 2nd ed., Wiley.
\bibitem{SA_BB} Bruce, P., Bruce, A. [2017], Practical Statistics for Data Scientists: 50 Essential Concepts, O'Reilly. 
\bibitem{SA_SS} Sivia, D.S., Skilling, J. [2006], Data Analysis: a Bayesian Tutorial, 2nd ed., Oxford. 
\bibitem{SA_R} Rizzo, M.L. [2007], Statistical Computing with R, CRC Press.
\bibitem{SA_Re} Reinhart, A. [2015], Statistics Done Wrong: the Woefully Complete Guide, No Starch Press. 
\bibitem{SA_HMC} Hogg, R., McKean, J., Craig, A., [2005], Introduction to Mathematical Statistics, 6th ed., Pearson. 
\bibitem{SA_JW} Johnson, R., Wichern, D., [2007], Applied Multivariate Statistical Analysis, 6th ed., Pearson. 
\bibitem{SA_M} Montegomery, D., [2009], Introduction to Mathematical Statistics, 7th ed., Wiley.
\bibitem{SA_1} \newhref{https://en.wikipedia.org/wiki/Naive\_Bayes\_classifier}{https://en.wikipedia.org/wiki/Naive\_Bayes\_classifier}
\bibitem{SA_2} \newhref{https://en.wikipedia.org/wiki/Hill\_equation\_(biochemistry)}{https://en.wikipedia.org/wiki/Hill\_equation\_(biochemistry)}
\bibitem{DAL_DSML} Boily, P., Schellinck, J. [2020], \textit{Machine Learning 101}, Data Science Report Series, data-action-lab.com.
\bibitem{CQADS_IBS} Hagiwara, S., Boily, P. [2014], \textit{Covariance Analysis of Irritable Bowel Syndrome Study II},  CQADS internal report. 
\bibitem{DSRS_BDA} Ghashim, E., Boily, P. [2020], \textit{A Soft Introduction to Bayesian Data Analysis}, Data Science Report Series, data-action-lab.com.
\bibitem{JWHT} James, G., Witten, D., Hastie, T., Tibshirani, R. [2013], \textit{An Introduction to Statistical Learning, with Applications in R}, Springer. 
\bibitem{Jack} \newhref{https://en.wikipedia.org/wiki/Jackknife\_resampling}{https://en.wikipedia.org/wiki/Jackknife\_resampling}
\end{thebibliography}