\newpage\phantomsection
\begin{thebibliography}{99}
\bibitem{TS_Mi} A.Milhoj, Practical Time Series Analysis Using SAS, SAS Institute. 
\bibitem{TS_TSAB} Time Series Analysis Branch, Guide to Seasonal Adjustment with X-12-ARIMA,  Office for National Statistics, UK. 
\bibitem{TS_CD} W.S.Cleveland, S.J.Devlin [1982], Calendar Effects in Monthly Time Series: Modeling and Adjustment, J.Am.Stat.Assoc., Vol. 77, no. 279, pp. 520-528.
\bibitem{TS_AEI} Estimating and Removing the Effects of Chinese New Year and Ramadan to Improve the Seasonal Adjustment Process, Australian Economic Indicators, November 2005.
\bibitem{TS_BH} P.Boily, Y.Huang [2013], Analysis of Fluidity Indicators and Seasonality Adjustment for Containers Transit Times in a Multi-Modal Supply Chain Network, Centre for Quantitative Analysis and Decision Support. 
\bibitem{TS_SS} R.H.Shumway, D.S.Stoffer [2010], Time Series Analysis and its Applications, Springer.
\bibitem{TS_L} R.Lindeke, Forecasting Models, Lecture Notes.
\bibitem{TS_S} N.Silver [2012], The Signal and the Noise: Why So Many Predictions Fail - and Others Don't, Penguin Publishing.
\bibitem{TS_M} D.Meko, Notes on Detrending, University of Arizona (online).
\bibitem{TS_Kalman} Wikipedia's entry on the Kalman Filter 
\bibitem{TS_F} D.S.C.Fung, Methods for the Estimation of Missing Values in Time Series    
\bibitem{TS_AHZ} O.Anava, E.Hazan, A.Zeevi, Online Time Series Prediction with Missing Data 
\bibitem{TS_Matlab} MATLAB's fillts method (http://www.mathworks.com/help/finance/fillts.html)
\bibitem{TS_Honaker} J.Honaker, G.King, What to do about Missing Values in Time Series Cross-Section Data
\bibitem{TS_HLB} J.Honaker, G.King, M.Blackwell, Amelia II: a Program for Missing Data 
\bibitem{TS_Pekar} B.Pekar, Automating Time Series Analysis - A Case-based Reasoning and Web Services \bibitem{TS_HK} R.J.Hyndman, Y.Khandakar, Automatic Time Series Forecasting: The forecast Package in R 
\bibitem{TS_Ashley} J.D.Ashley, Why Seasonal Adjustment, Catherine Hood Consulting (online).
\bibitem{TS_Hood} C.C.Hood, Seasonal Adjustment and Time Series FAQ, Catherine Hood Consulting (online).
\bibitem{TS_Monsell} B.C.Monsell, A Painless Introduction to Seasonal Adjustment, U.S. Census Bureau.
\bibitem{TS_Lata} H.A.Latane [1942], Seasonal Factors Determined by Difference from Average of Adjacent Months, J.Am.Stat.Assoc, Dec.
\bibitem{TS_FH} D.F.Findley, C.C.Hood, X-12-ARIMA and its Application to Some Italian Indicator Series,  U.S. Bureau of the Census.
\bibitem{TS_FMBOC} D.F.Findley, B.C.Monsell, Bell, Otto and Chen [1998], New Capabilities and Methods of the X-12-ARIMA Seasonal Adjustment Program, U.S. Bureau of the Census. 
\bibitem{TS_ICTSA} An Introductory Course on Time Series Analysis, Australian Bureau of Statistics. 
\bibitem{TS_SAETS} Seasonal Adjustment of Economic Time Series, Singapore Department of Statistics.
\bibitem{TS_JL} T.Jackson, M.Leonard, Seasonal Adjustment Using The X12 Procedure, SAS Institute.
\bibitem{TS_CE} A.J.Calise, J.Earley, Detecting Structural Change Using SAS/ETS Procedures.

\bibitem{TS_AA} Ratnadip Adhikari, R. K. Agrawal An Introductory Study on Time Series Modeling and Forecasting
\bibitem{TS_SH} Siegfried Heiler, A Survey on Nonparametric Time Series Analysis
\bibitem{TS_DWDFZZ} Rui Ding, Qiang Wang, Yingnong Dang, Qiang Fu, Haidong Zhang, Dongmei Zhang, YADING: Fast Clustering of Large-Scale Time Series Data
\bibitem{TS_AM} Paul L. Anderson and Mark M. Meerschaert, Parameter Estimation for Periodcally Stationary Time Series
\bibitem{TS_YKMSS} Shiming Yang, Konstantinos Kalpakis, Colin F. Mackenzie, Lynn G. Stansbury, and Deborah M. Stein, Online recovery of missing values in vital signs data streams using low-rank matrix completion
\bibitem{TS_JG} Nan Jiang and Le Gruenwald, Estimating Missing Data in Data Streams
\bibitem{TS_UHD} Thomas Url, Rob J Hyndman, Alexander Dokumentov, Long-term forecasts of age-specific participation rates with functional data models  
\bibitem{TS_online} \newhref{https://onlinecourses.science.psu.edu/stat510/node/78}{https://onlinecourses.science.psu.edu/stat510/node/78}
\bibitem{TS_Hyn} Rob J Hyndman 's blog   
\bibitem{TS_LV} S.Lenser and M.Veloso, \textit{Non-Parametric Time Series Classification}, Carnegie-Mellon University, 2007
\bibitem{TS_Mah} H.F.F.Mahmoud, \textit{Parametric versus Semi/nonparametric Regression Models}, Virginia Polytechnic Institute and State University Department of Statistics, LISA short course series- July 23, 2014
\end{thebibliography}





