\newpage\phantomsection
\begin{thebibliography}{99}
\bibitem{OPT_B} Bertsekas, D.P. [2016], \textit{Nonlinear Programming}, Athena Scientific
Optimisation and Computation Series, Athena Scientific.
\bibitem{OPT_BT} Bertsimas, D.P.,  Tsitsiklis, J. [1997],  \textit{Introduction to
Linear Optimisation} (1st ed.), Athena Scientific.
\bibitem{OPT_C} Cornu\'ejols, G. [2007], ``Valid Inequalities for Mixed Integer Linear
Programs,'' \textit{Math. Program.} 112 (1), Secaucus, NJ, USA, 
Springer, 3--44.
\bibitem{OPT_W} Williams, H.P. [2013], \textit{Model Building in Mathematical Programming}, Wiley.
\bibitem{OPT_Z} Zhu, J., \textit{Performance Evaluation and Benchmarking Using DEA}. 
%\bibitem{OPT_FFWP} J. Fiallos, K. Farion, W. Michalowski, J. Patrick, \textit{Evaluating Emergency Physicians: Data Envelopment Analysis Approach}.  
\bibitem{OPT_MPSP} C. Mar-Molinero, D. Prior, M.-M. Segovia, F. Portillo, \textit{On Centralized Resource Utilization And Its Reallocation By Using DEA}, 18 February 2012.  
\bibitem{OPT_LM} M. Laguna, J. Marklund, \textit{Business Process Modeling, Simulation and Design}, Chapter  11. 
\bibitem{OPT_T} M. Trick, \textit{Data Envelopment Analysis} notes.  
\bibitem{OPT_DEA} Wikipedia article on \textit{Data Envelopment Analysis}. 
\bibitem{OPT_H} R. M. Hayes, \textit{Data Envelopment Analysis}, 2005. 
\bibitem{OPT_MS} R. Markovits-Somogy, \textit{Ranking Efficient and Inefficient Decision Making Units In Data Envelopment Analysis}, 2011. 
\bibitem{OPT_SZ} H. D. Sherman, J. Zhu, \textit{Service Productivity Management: Improving Service Performance using Data Envelopment Analysis (DEA)}, 2006. 
\bibitem{OPT_F} J. Fiallos, \textit{A Model for Performance Evaluation of Emergency Department Physicians}, 2014 
\begin{thebibliography}{99}