\phantomsection
\begin{thebibliography}{99}

\bibitem{BDA_B} Bayes, T. [1763], An Essay towards solving a Problem in the Doctrine of Chances, {\it Phil. Trans. Royal Society London}.
\bibitem{BDA_G} Gill, J. [2002],  Bayesian Methods for the Social and Behavioral Sciences, Boca Raton, Florida: CRC Press.  
\bibitem{BDA_H} 
Hitchcock, D. [2014], Introduction to Bayesian Data Analysis, Department of Statistics, University of South Carolina, US,  course notes.  
\bibitem{BDA_B1} Berger, J.O. [1985],  Statistical Decision Theory and Bayesian Analysis, Springer-Verlag, New York, 2nd edition.
\bibitem{BDA_R} Robert, C.F. [2006], Le choix bay\'esien - Principes et pratique, Springer-Verlag France, Paris.

\bibitem{BDA_K1} Kruschke, J.K. [2009], Highlighting: A canonical experiment. In B. Ross (Ed.), \textit{The psychology of learning and motivation} (Vol. 51, pp. 153–185). Elsevier  Academic Press. 

\bibitem{BDA_SS} Sivia, D.S., Skilling, J. [2006], Data Analysis: A Bayesian Tutorial (2nd ed.), Oxford Science.
\bibitem{BDA_S} Silver, N. [2012], The Signal and the Noise, Penguin.
\bibitem{BDA_J} Jaynes, E.T. [2003], Probability Theory: the Logic of Science, Cambridge Press. 
\bibitem{BDA_K} Kruschke, J.K. [2011], Doing Bayesian Data Analysis: a Tutorial with R, JAGS, and Stan (2nd ed.), Academic Press
\bibitem{BDA_Barber} Barber, D. [2012], Bayesian Reasoning and Machine Learning, Cambridge Press.
\bibitem{BDA_GCSDVR} Gelman, A., Carloin, J.B., Stern, H.S., Dunson, D.B., Vehtari, A., Rubin, D.B. [2013], Bayesian Data Analysis (3rd ed.), CRC Press.
\bibitem{BDA_B2} Baath, R. [2015], Introduction to Bayesian Data Analysis with R, UseR!
\bibitem{BDA_O} Oliphant, T.E. [2006], A Bayesian perspective on estimating mean variance, and standard-deviation from data, All Faculty Publications 278, BYU. 

\bibitem{BDA_N1} \newhref{https://people.eecs.berkeley.edu/~jordan/courses/260-spring10/lectures/lecture9.pdf}{Reference Priors and Maximum Entropy} (lecture notes)

\bibitem{BDA_N2}
\newhref{http://web.stanford.edu/~rjohari/teaching/notes/226_lecture16_inference.pdf}{Bayesian Inference} (lecture notes)

\bibitem{BDA_N3}
\newhref{http://www.biostat.umn.edu/~ph7440/pubh7440/Lecture8Ppt.pdf}{MCMC algorithms for fitting Bayesian models} (lecture notes)

\bibitem{BDA_N4} \newhref{http://www.mit.edu/~ilkery/papers/MetropolisHastingsSampling.pdf}{Bayesian Inference: Metropolis-Hastings Sampling}

\bibitem{BDA_N5}
\newhref{http://www.scholarpedia.org/article/Bayesian_statistics}{Bayesian Statistics} (scholarpedia article)


\bibitem{BDA_N6}
\newhref{http://www.statisticshowto.com/bayes-theorem-problems/}{Bayes’ Theorem Problems, Definition and Examples} (statisticshowto.com)

\bibitem{BDA_N7}
\newhref{https://making.lyst.com/2014/05/10/bayesian-ab-testing/}{Bayesian AB Testing} (Lyst)

\bibitem{BDA_N8}
\newhref{https://www.datascience.com/blog/introduction-to-bayesian-inference-learn-data-science-tutorials}{Introduction to Bayesian Inference} (datascience.com) 

\bibitem{BDA_N9}
\newhref{http://moreisdifferent.com/blog/2015/12/28/cleamaximum-entropy-priors/}{Maximum Entropy Priors} (moreisdifferent.com)

\bibitem{BDA_N10}
\newhref{http://www.di.fc.ul.pt/~jpn/r/maxent/maxent.html}{Maximum Entropy}

\bibitem{BDA_N11}
\newhref{https://theoreticalecology.wordpress.com/2011/12/09/mcmc-chain-analysis-and-convergence-diagnostics-with-coda-in-r/}{MCMC chain analysis and convergence diagnostics with coda in R} (theoreticalecology.wordpress.com)


\bibitem{BDA_N12}
\newhref{https://theoreticalecology.wordpress.com/2010/09/17/metropolis-hastings-mcmc-in-r/}{A simple Metropolis-Hastings MCMC in R} (theoreticalecology.wordpress.com)
\bibitem{BDA_N122} \newhref{https://en.wikipedia.org/wiki/Conjugate_prior}{Conjugate Priors} (Wikipedia)
\bibitem{BDA_N13}
\newhref{http://rpubs.com/rasmusab/exercise_1_user_2015_bayes_tutorial}{Bayesian A/B Testing for Swedish Fish Incorporated} (tutorial)

\bibitem{BDA_N14}
\newhref{https://www.youtube.com/watch?v=5P58wHbWXBU}{Maximum Entropy Methods Tutorial: A Simple Example: The Taxicab} (video)  

\bibitem{BDA_N15}
\newhref{https://www.youtube.com/watch?v=kw4deNTVO7A}{Maximum Entropy Methods Tutorial: MaxEnt applied to Taxicab Example Part 1} (video)

\bibitem{BDA_N16}
\newhref{https://docs.pymc.io/}{PYMC3} (documentation)

\bibitem{BDA_CGM} Chipman, H.A., George, E.I., McCulloch, R.E. [2010],  BART: Bayesian additive regression trees, Annals of Applied Statistics 6 (1), 266–298.  

\bibitem{BDA_CGM2} Chipman, H.A., George, E.I., McCulloch, R.E. [1998], Bayesian CART model search (with discussion and a rejoinder by the authors), J. Amer. Statist. Assoc. 93 935–960. 

\bibitem{BDA_HRPP} Hernandez, B., Raftery, A.E., Pennington, S.R.,  Parnell, A.C. [2015], Bayesian Additive Regression Trees Using Bayesian Model Averaging, Technical Report no. 636, Department of Statistics, University of Washington. 

\bibitem{BDA_Ka} Kabacoff, R.I. [2011], R in Action, Second Edition: Data analysis and graphics with R.

\bibitem{BDA_BTCRAN} \newhref{http://ftp.auckland.ac.nz/software/CRAN/doc/packages/BayesTree.pdf}{BayesTree} (CRAN package)

\bibitem{BDA_MCC}
\newhref{http://www.stat.rice.edu/~jrojo/4th-Lehmann/slides/mcculloch.pdf}{BART} (slides)
\bibitem{BDA_K2} \newhref{http://www.indiana.edu/~kruschke/DoingBayesianDataAnalysis/Programs/}{Doing Bayesian Data Analysis} (R Code).
\bibitem{BDA_NNN} \newhref{http://bayesian-intelligence.com/bwb/2012-03/sally-clark-is-wrongly-convicted-of-murdering-her-children/}{Sally Clark is Wrongly Convicted of Murdering Her Children} (Bayesians Without Borders).
\bibitem{BDA_W} Wilkinson, D.J. [2007], \newhref{http://citeseerx.ist.psu.edu/viewdoc/download?doi=10.1.1.578.9403&rep=rep1&type=pdf}{Bayesian Methods  in Bioinformatics and Computational Systems Biology}, Briefings in Bioinformatics, v.8, n.2, 109--116.
\bibitem{BDA_Poldrack} Poldrac, R.A. [2006], `Can cognitive processes be inferred from neuroimaging data?, \textit{Trends Cogn.\@ Sci.} 10(2):59-63. 
\end{thebibliography}







