\phantomsection
\begin{thebibliography}{99}
\bibitem{DP_C}
Chapman, A. [2005], Principles and Methods of Data Cleaning - Primary Species and Species-Occurrence Data, Report for the Global Biodiversity Information Facility, Copenhagen.
\bibitem{DP_vB}van Buuren, S. [2012], Flexible Imputation of Missing Data, CRC Press, Boca Raton.
\bibitem{DP_Shinnie}Hagiwara, S. [2012], Nonresponse Error in Survey Sampling - Comparison of Different Imputation Methods, Honours Thesis, Carleton University, Ottawa.
\bibitem{DP_RLVHS}Raghunathan, T., Lepkowski, J., Van Hoewyk, J. and Solenberger, P. [2001], A Multivariate Technique for Multiply Imputing Missing Values Using a Sequence of Regression Models, Survey Methodology, v.27, n.1, pp.85-95, Statistics Canada, Catalogue no. 12-001.
\bibitem{DP_R}Rubin, D.B. [1987], Multiple Imputation for Nonresponse in Surveys, Wiley, New York.
\bibitem{DP_KNNL}Kutner, M., Nachtsheim, C., Neter, J. and Li, W. [2004], Applied Linear Statistical Models, 5th ed., McGraw-Hill/Irwin, New York.
\bibitem{DP_GS}Green, S. and Salkind, N. [2011], Using SPSS for Windows and Macintosh - Analyzing and Understanding Data, 6th ed., Prentice Hall, Upper Saddle River.
\bibitem{DP_DC}Wikipedia entry for Data Cleansing 
\bibitem{DP_I}Wikipedia entry for Imputation
\bibitem{DP_O}Wikipedia entry for Outliers
\bibitem{DP_T}Torgo, L. [2017], Data Mining with R (2nd edition), CRC Press.
\bibitem{DP_M}McCallum, Q.E. [2013], Bad Data Handbook, O'Reilly.
\bibitem{DP_KJ}Kazil, J., Jarmul, K. [2016], Data Wrangling with Python, O'Reilly
\bibitem{DP_dJvdL}de Jonge, E., van der Loo, M. [2013], An Introduction to Data Cleaning with R, Statistics Netherlands.
\bibitem{DP_P}Pyle, D. [1999], Data Preparation for Data Mining, Morgan Kaufmann Publishers.
\bibitem{DP_WI}Weiss, S.M., Indurkhya, I. [1999], Predictive Data Mining: A Practical Guide, Morgan Kaufmann Publishers.
\bibitem{DP_B}Buttrey, S.E. [2017], A Data Scientist's Guide to Acquiring, Cleaning, and Managing Data in R, Wiley.
\bibitem{DP_A}Aggarwal, C.C. [2013], Outlier Analysis, Springer.
\bibitem{DP_CBK}Chandola, V., Banerjee, A., Kumar, V. [2007], Outlier detection: a survey, Technical Report TR 07-017, Department of Computer Science and Engineering, University of Minnesota.
\bibitem{DP_HA}Hodge, V., Austin, J. [2004], A survey of outlier detection methodologies, Artif.Intell.Rev., 22(2):85-126.
\bibitem{DP_FNWO}Feng, L., Nowak, G., Welsh, A.H., O'Neill, T. [2014], imputeR: a general imputation framework in R.
\bibitem{DP_S}Steiger, J.H. , Transformations to Linearity, lecture notes.
\bibitem{DP_W}Wood, F., Remedial Measures Wrap-Up and Transformations, lecture notes. 
\bibitem{DP_DKS}Dougherty, J., Kohavi, R., Sahami, M. [1995], Supervised and unsupervised discretization of continuous features, in Machine Learning: Proceedings of the Twelfth International Conference, Prieditis, A., Russell, S. (eds), Morgan Kaufmann Publishers. 
\bibitem{DP_OW}Orchard, T., Woodbury, M. [1972], A Missing Information Principle: Theory and Applications, Berkeley Symposium on Mathematical Statistics and Probability, University of California Press.  
\bibitem{DP_HPC}Height Percentile Calculator, by Age and Country, https://tall.life/height-percentile-calculator-age-country/ 
\bibitem{DP_BUPA} Dua, D., Karra Taniskidou, E. [2017], Liver Disorders dataset, UCI Machine Learning Repository.
\bibitem{DP_SS} https://simplystatistics.org/2014/10/24/an-interactive-visualization-to-teach-about-the-curse-of-dimensionality/ 
\end{thebibliography}
%\setboolean{@twoside}{false}
%\includepdf[pages={1-9},offset={50 -40}]{documents/BAC_jur.pdf}
%\setboolean{@twoside}{true}