\phantomsection
\begin{thebibliography}{99}
\bibitem{DV_M2} Malamed, C., \newhref{http://understandinggraphics.com}{Understanding Graphics}.
\bibitem{DV_KW} Krygier, J., Wood, D., [2016], Making Maps: A Visual Guide to Map Design for GIS, Guilford Press.
\bibitem{DV_IDV} \newhref{https://en.wikipedia.org/wiki/Interactive_data_visualization}{Interactive Data Visualization} on Wikipedia.
\bibitem{DV_S} Simmon, R. [2013], \newhref{https://earthobservatory.nasa.gov/blogs/elegantfigures/2013/03/14/is-animation-an-effective-tool-for-data-visualization/}{Is animation an effective tool for data visualization?}, NASA's Earth Observatory. 
\bibitem{DV_H} Healey, C.G., \newhref{https://www.csc2.ncsu.edu/faculty/healey/PP/}{Perception in Visualization}
\bibitem{DV_P} \newhref{http://dataphys.org/list/}{Data Physicalizations}
\bibitem{DV_T1} Tufte, E. [2001], The Visual Display of Quantitative Information, Graphics Press.
\bibitem{DV_H2} Hu, D. [1954], How to Lie With Statistics, Norton.
\bibitem{DV_T2} Tufte, E. [2008], Beautiful Evidence, Graphics Press.
\bibitem{DV_NK} Nussbaumer Knaflic, C. [2015], Storytelling with Data, Wiley.
\bibitem{DV_C1} Cairo, A. [2013], The Functional Art, New Riders.
\bibitem{DV_C2} Cairo, A. [2016], The Truthful Art, New Riders.
\bibitem{DV_M} Meireilles, I. [2013], Design for Information, Rockport.
\bibitem{DV_50} \newhref{http://www.webdesignerdepot.com}{50 Great Examples of Data Visualization}. 
\bibitem{DV_K} Kirk, A., \newhref{http://www.visualisingdata.com}{Visualising Data}.
\bibitem{DV_Y} Yau, N., \newhref{http://flowingdata.com}{FlowingData}. 
\bibitem{DV_DV} \newhref{https://en.wikipedia.org/wiki/Data_visualization}{Data Visualization} on Wikipedia.
\bibitem{DV_MG} \newhref{https://en.wikipedia.org/wiki/Misleading_graphs}{Misleading Graphs} on Wikipedia.
\bibitem{DV_P2} Prabhakaran, S., \newhref{http://r-statistics.co/Top50-Ggplot2-Visualizations-MasterList-R-Code.html}{Top 50 ggplot2 Visualizations}. 
\bibitem{DV_M3} Miller, M. [2017], The problem with Interactive graphics, Co.Design
\bibitem{DV_W} Wickham, H. [2016], ggplot2: Elegant Graphics for Data Analysis (2nd ed), Springer.
\bibitem{DV_G} Gorelik, B., Data Visualization (blog).
\bibitem{DV_AIM} Miller, A.I. [2012], \newhref{https://www.theguardian.com/science/blog/2012/jul/17/henri-poincare-einstein-picasso?newsfeed=true}{Henri Poincar\'e: the unlikely link between Einstein and Picasso}, in The Guardian. 
\bibitem{DV_WSC} Wexler, S., Shaffer, J., Cotgreave, A. [2017], the Big Book of Dashboards, Wiley. 
\end{thebibliography}