\phantomsection
\begin{thebibliography}{99}
\bibitem{QS_Erlang} Erlang, A.K. [1909], ``The Theory of Probabilities and Telephone Conversations'', Nyt Tidsskrift for Matematik B, 20, 33.
\bibitem{QS_Berry} Berry, R. [2002], ``Queueing Theory and Applications'', 2nd Edition, PWS, Kent Publishing.
\bibitem{QS_W} Winston, W.L. [2004], Operations Research: Applications and Algorithms, 2nd ed., PWS-Kent Publishing, Boston.
\bibitem{QS_R} Ross, S.M. [2014], Introduction to Probability Models,  11th ed., Academic Press. 
\bibitem{QS_1} NPTEL's \newhref{https://nptel.ac.in/courses/110/106/110106046/}{Services Operations Management}, Web Course, Module 9, Lecture 4.
\bibitem{QS_2} NPTEL's \newhref{https://nptel.ac.in/courses/110/106/110106046/}{Services Operations Management}, Web Course, Module 9, Lecture 5.
\bibitem{QS_3} Nicol, D.M., \newhref{http://dmnicol.web.engr.illinois.edu/ece541/slides/queueing.pdf}{Introduction to Queueing Theorey} lecture notes.
\bibitem{QS_4} \newhref{https://www.wisdomjobs.com/e-university/quantitative-techniques-for-management-tutorial-297/poisson-and-exponential-distributions-9931.html}{Quantitative Techniques for Management: Poisson and Exponential Distributions}, on wisdomjobs.com
\bibitem{QS_5}
Schwartz, B. [2016],  \newhref{https://www.percona.com/live/17/sites/default/files/the-essential-guide-to-queueing-theory.pdf}{The Essential Guide to Queueing Theory}, Vivid Cortex.
\bibitem{QS_K} Kendall, D.G. [1953], ``Stochastic Processes Occurring in the Theory of Queues and their Analysis by the Method of the Imbedded Markov Chain'', Ann.Math.Stat. 24 (3): 338.
\bibitem{QS_K1} Kleinrock, L. [1975], Queueing Systems, vol. 1, Wiley.
\bibitem{QS_GSTH} Gross, D., Shortle, J.F., Thompson, J.M., Harris, C.M. [2008], Fundamentals of Queueing Theory, 4th ed., Wiley.
\bibitem{QS_B} Burke, P.J. [1956], The Output of a Queueing System, Operations Reserach vol 4 (6): 699704.
\bibitem{QS_N} Newell, G.F. [1971], Applications of Queueing Theory, Chapman and Hall.
\bibitem{QS_Wa} Walrand, J. [1983], A probabilistic look at networks of quasi-reversible queues, IEEE Transactions on Information Theory, vol 29 (6): 825831.
\bibitem{QS_Wiki} \newhref{https://en.wikipedia.org/wiki/Queueing\_theory}{Queueing Theory} on Wikipedia.
\bibitem{QS_E} Erickson, W. [1973], Management Science and the Gas Shortage, Interfaces 4:47–51.
\end{thebibliography}



